A 3d curvilinear skeletonization algorithm with application to path tracing

### 2012-09-14 application_to_path_tracing.tex
Inserting new biblio

\begin{align*}
L(x \rightarrow \Theta) &= L_e(x \rightarrow \Theta) + \int_{\Phi \in \Omega_x} f_s(x, \Theta \leftrightarrow \Phi) L(r(x, \Phi) \rightarrow -\Phi) d\omega_\Phi \\
&= L_e(x \rightarrow \Theta) + L_r(x \rightarrow \Theta)
\end{align*}

@@

This integrand expresses an intuitive idea: the reflected radiance from $x$ towards the camera is the result of computing all incoming luminosity on $x$ scaled by a factor which depends on the material on $x$ and the angle of the ray going from the camera to $x$. The most common method used to estimate the integral is the Monte-Carlo integration which provides the following:

@@

Given a point $x$ and a direction $\Theta$ we want to compute $L(x \rightarrow \Theta)$ and then sample the hemisphere $\Omega_x$. We search for the nearest skeleton node $n$ and its importance point $imp_n$. We sample the hemisphere with a power-cosine pdf centered on $\overrightarrow{ximp_n}$:

\begin{equation*}
p_{skel}(\Phi) = \frac{s + 1}{2\pi} cos^s \alpha
\end{equation*}

with $\alpha$ the angle between $\overrightarrow{ximp_n}$ and $\Phi$, $s$ being a parameter called skeleton strength. The higher $s$ is, the more we sample close $\overrightarrow{ximp_n}$.
\begin{figure}[thp]
\begin{center}
\includegraphics[scale=0.17]{images/four_scenes_for_dgci.png}
\caption{\label{fig:results}Four images comparing the classic path tracing (image $a$ and $c$) and our method (image $b$ and $d$). Note the noise reduction of our method in the left wall of images $a$ and $b$, and on the floor on image $c$ and $d$.}
\end{center}
\end{figure}

@@

@@

We presented an application of our skeletonization algorithm for global illumination. Our strategy works well, it reduces noise by taking into account the distribution of energy in the scene. One of the problems is that we take into account only one importance direction for sampling, totally ignoring the BRDF and the cosine factor. A solution called Multiple Importance Sampling will allow us to combine different strategies into one.

>>>>

\begin{align*}
L(x \rightarrow \Theta) &= L_e(x \rightarrow \Theta) + \int_{\Phi \in \Omega_x} f_s(x, \Theta \leftrightarrow \Phi) L(r(x, \Phi) \rightarrow -\Phi) d\omega_\Phi
\end{align*}

@@

This integrand expresses an intuitive idea: the reflected radiance from $x$ towards the camera is the result of computing all incoming luminosity on $x$ scaled by a factor which depends on the material on $x$ and the angle of the ray going from the camera to $x$. The most common method used to estimate the integral, denoted by $L_r(x \rightarrow \Theta)$, is the Monte-Carlo integration which provides the following:

@@

Given a point $x$ and a direction $\Theta$ we want to compute $L(x \rightarrow \Theta)$ and then sample the hemisphere $\Omega_x$. We search for the nearest skeleton node $n$ and its importance point $imp_n$. We sample the hemisphere with a power-cosine pdf centered on $\overrightarrow{ximp_n}$:
\begin{equation*}
p_{skel}(\Phi) = \frac{s + 1}{2\pi} cos^s \alpha
\end{equation*}
with $\alpha$ the angle between $\overrightarrow{ximp_n}$ and $\Phi$, $s$ being a parameter called skeleton strength. The higher $s$ is, the more we sample close $\overrightarrow{ximp_n}$.

@@

Some results are presented in figure~\ref{fig:results} where we can see the decrease in noise compare to the regular path tracing. We computed the MSE value for different scenes that are presented in table~\ref{tab:timing}

\begin{figure}[tbhp]
\begin{center}
\includegraphics[scale=0.17]{images/four_scenes_for_dgci.png}
\caption{\label{fig:results}Four images comparing the classic path tracing (image $a$ and $c$) and our method (image $b$ and $d$). Note the noise reduction of our method in the left wall of images $a$ and $b$, and on the floor on image $c$ and $d$.}
\end{center}
\end{figure}

\begin{table}[t!]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Scene & fig.\ref{fig:redcorridor} & fig.\ref{fig:examples} far left & fig.\ref{fig:examples} far right \\
\hline
MSE 100& 145 / 57 & 301 / 156 & 881 / 826 \\
\hline
MSE 40& 434 / 260 & 924 / 628 & 2678 / 2570 \\
\hline
\end{tabular}
\caption{Timing(s) to reach an MSE of 100 and 40 against reference images. In each cell, the left number is for the standard path tracing, the right one  our method}
\label{tab:timing}
\end{table}

@@

We presented in this article a new skeletonization algorithm that both preserves geometrical features of objects and produces a pure curvilinear skeleton. These two properties allow us to improve the path tracing algorithm in guiding the rays towards the main illuminated area of the scene. Our algorithm is faster and produce less noise than the classical path tracing method.
